\documentclass[12pt, letterpaper]{article}
\usepackage[titletoc,title]{appendix}
\usepackage{booktabs}
\usepackage[margin=1in]{geometry}
\usepackage[linkcolor=blue,
			colorlinks=true,
			urlcolor=blue,
			pdfstartview={XYZ null null 1.00},
			pdfpagemode=UseNone,
			citecolor={bluish},
			pdftitle={blacklight}]{hyperref}

%\newcites{SI}{SI References}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{float}
\usepackage{placeins}

\usepackage{geometry}  % see geometry.pdf on how to lay out the page. There's lots.
\geometry{letterpaper} % This is 8.5x11 paper. Options are a4paper or a5paper or other...
\usepackage{graphicx}  % Handles inclusion of major graphics formats and allows use of
\usepackage{units}
\usepackage{amsfonts,amsmath,amsbsy}
\usepackage{amsxtra}
\usepackage{verbatim}
%\setcitestyle{round,semicolon,aysep={},yysep={;}}
\usepackage{setspace} % Permits line spacing control. Options are:
%\doublespacing
%\onehalfspace
%\usepackage{sectsty}    % Permits control of section header styles
\usepackage{pdflscape}
\usepackage{fancyhdr}   % Permits header customization. See header section below.
\usepackage{url}        % Correctly formats URLs with the \url{} tag
\usepackage{xurl}
\usepackage{fullpage}   %1-inch margins
\usepackage{multirow}
\usepackage{verbatim}
\usepackage{rotating}
\setlength{\parindent}{3em}

%\usepackage[T1]{fontenc}
%\usepackage[bitstream-charter]{mathdesign}

\usepackage{chngcntr}
\usepackage{longtable}
\usepackage{adjustbox}
\usepackage{dcolumn}
\usepackage{tabularx}

\usepackage{lineno}

\usepackage[12pt]{moresize}

\usepackage{pdfpages}

% https://tex.stackexchange.com/questions/611786/misplaced-noalign-because-input-before-booktabs-rule
% I was getting Misplaced \noalign. \bottomrule on my laptop
% but not on my desktop...
% Comment out for older LaTeX versions
%\iffalse
\ExplSyntaxOn
\cs_new:Npn \expandableinput #1
{ \use:c { @@input } { \file_full_name:n {#1} } }
\AddToHook{env/tabular/begin}
{ \cs_set_eq:NN \input \expandableinput }
\ExplSyntaxOff
%\fi


\usepackage[nameinlink, capitalize, noabbrev]{cleveref}

\def\citeapos#1{\citeauthor{#1}'s (\citeyear{#1})}

\makeatother

\usepackage{footmisc}
\setlength{\footnotesep}{\baselineskip}
\makeatother
\renewcommand{\footnotelayout}{\footnotesize \onehalfspacing}
%https://tex.stackexchange.com/a/68242
%prevent footnotes splitting over pages
\interfootnotelinepenalty=10000


% Colors
\usepackage{color}

\newcommand{\bch}{\color{blue}\em  }   % begin change
\newcommand{\ying} {\color{orange}\em  }   % begin change
\newcommand{\bgcd} {\color{purple}\em }
\newcommand{\ech}{\color{black}\rm  }    % end change

\newcommand{\note}[1]{\textcolor{orange}{#1}}

% Caption
% Caption
\usepackage[
    skip            =0pt,
    labelfont       =bf, 
    font            =small,
    textfont        =small,
    figurename      =Figure,
    justification   =justified,
    singlelinecheck =false,
    labelsep        =period]
{caption}
%\captionsetup[subtable]{font=small,skip=0pt}
\usepackage{subcaption}

% tt font issues
% \renewcommand*{\ttdefault}{qcr}
\renewcommand{\ttdefault}{pcr}

\usepackage{tocloft}

\newcommand{\detailtexcount}[1]{%
  \immediate\write18{texcount -merge -sum -q #1.tex output.bbl > #1.wcdetail }%
  \verbatiminput{#1.wcdetail}%
}

\newcommand{\quickwordcount}[1]{%
  \immediate\write18{texcount -1 -sum -merge -q #1.tex output.bbl > #1-words.sum }%
  \input{#1-words.sum} words%
}

\newcommand{\quickcharcount}[1]{%
  \immediate\write18{texcount -1 -sum -merge -char -q #1.tex output.bbl > #1-chars.sum }%
  \input{#1-chars.sum} characters (not including spaces)%
}

\title{Inferring Support from Endorsement Experiments\thanks{\href{http://github.com/soodoku/endorsement}{http://github.com/soodoku/endorsement}.}}

\author{Gaurav Sood\thanks{Gaurav can be reached at \href{mailto:gsood07@gmail.com}{\footnotesize{\texttt{gsood07@gmail.com}}}}\vspace{.5cm}}

\date{\today}

\begin{document}

\maketitle

\section{Introduction}

Endorsement experiments are a popular tool in political science and survey research to estimate latent attitudes toward controversial political actors, such as militant groups or unpopular politicians. These experiments randomly assign a group endorsement to a policy and measure how the endorsement affects respondents' support for the policy. While researchers typically report the average treatment effect (ATE), interpreting what this aggregate measure reveals about the distribution of attitudes toward the endorsing group is nontrivial.

This paper develops a framework for inferring bounds on support for endorsing groups from observed treatment effects. We show how to derive theoretical limits on the proportion of supporters and present computational methods for estimating empirical bounds using optimization techniques.

\section{Basic Framework and Assumptions}

\subsection{Setup}
Consider a standard between-subjects endorsement experiment where respondents are randomly assigned to either:
\begin{itemize}
\item \textbf{Treatment}: ``Do you support this policy? [Group Y endorses this policy.]''
\item \textbf{Control}: ``Do you support this policy?''
\end{itemize}

We assume respondents fall into two categories with binary policy preferences:
\begin{itemize}
\item \textbf{Supporters} (proportion $p$): Switch from opposing to supporting the policy when their favored group endorses it (effect: $0 \to 1$, so $\delta = +1$)
\item \textbf{Opponents} (proportion $1-p$): Switch from supporting to opposing the policy when the disliked group endorses it (effect: $1 \to 0$, so $\delta = -1$)
\end{itemize}

In this binary framework, the individual treatment effect $\delta_i \in \{-1, 0, +1\}$ represents whether respondent $i$ switches their binary support/oppose response due to the endorsement.

\subsection{Symmetric Effects Model}
Under the binary switching assumption, the ATE can be written as:
\begin{align}
\text{ATE} &= p \cdot (+1) + (1 - p) \cdot (-1) \label{eq:ate_basic}\\
&= p - (1-p) = 2p - 1 \label{eq:ate_simplified}
\end{align}

Solving for $p$, the proportion of group supporters:
\begin{align}
p &= \frac{\text{ATE} + 1}{2} \label{eq:p_solve}
\end{align}

This binary framework provides a clean interpretation: the ATE directly maps to the difference between supporters and opponents, with $\text{ATE} = 0$ indicating equal proportions ($p = 0.5$).

\section{Adjusting for Partial Awareness}

In many contexts, not all respondents have strong opinions about the endorsing group. Let $q$ represent the fraction of the population with genuine attitudes toward the group. Under the binary switching model:

\begin{align}
\text{ATE} &= q \cdot (2p - 1) \label{eq:ate_partial}
\end{align}

Where $p$ now represents the proportion of \emph{opinion-holders} who support the group. Solving for $p$:
\begin{align}
p &= \frac{\text{ATE}}{2q} + \frac{1}{2} \label{eq:p_partial}
\end{align}

\subsection{Example: Militant Group Support in Pakistan}
Consider an endorsement experiment with $\text{ATE} = -0.011$. If we assume that 70\% of respondents have genuine opinions about militant groups ($q = 0.7$), then:

\begin{align}
p &= \frac{-0.011}{2 \times 0.7} + 0.5 = \frac{-0.011}{1.4} + 0.5 \approx 0.492
\end{align}

This suggests that approximately 49.2\% of opinion-holders support the group—indicating slight net opposition, but nearly balanced attitudes among those with genuine opinions.

\section{Incorporating Baseline Support Information}

\subsection{Additional Constraints from Constant Term}
When we observe both the constant term ($\alpha$) and treatment effect ($\beta$) from the regression:
\begin{align}
\text{Support} = \alpha + \beta \cdot \text{Treatment} + \varepsilon
\end{align}

The constant term provides crucial additional information. If $\alpha = 0.8$ and $\beta = -0.011$, then:
\begin{itemize}
\item Control group average support = 0.8
\item Treatment group average support = 0.8 - 0.011 = 0.789
\end{itemize}

\subsection{Exact Solution Under Binary Complete Switching}
In our binary framework where supporters always switch (0→1) and opponents always switch (1→0), the analysis becomes straightforward:

\begin{itemize}
\item \textbf{Supporters in treatment:} Always end up at 1 (regardless of baseline)
\item \textbf{Opponents in treatment:} Always end up at 0 (regardless of baseline)  
\end{itemize}

Therefore, the treatment group average equals the proportion of supporters:
\begin{align}
\text{Treatment average} &= p \cdot 1 + (1-p) \cdot 0 = p \\
0.789 &= p
\end{align}

\textbf{Result: Exactly 78.9\% are supporters} under complete binary switching.

This is dramatically higher than our previous bound of 49.45\% because we now use information about baseline support levels, not just the treatment effect.

\subsection{Intuition}
The high baseline support (80\%) combined with a small negative treatment effect (-1.1 percentage points) is consistent with most people being supporters of the group. The slight decrease in average support occurs because:
\begin{itemize}
\item 78.9\% are supporters → always support policy in treatment
\item 21.1\% are opponents → always oppose policy in treatment  
\item Net effect: 78.9\% - 80\% = -1.1 percentage points
\end{itemize}

This interpretation suggests that despite negative average sentiment, a large majority actually supports the endorsing group.

\subsection{Sensitivity to Switching Assumptions}
This result depends critically on the complete switching assumption. If supporters and opponents make smaller adjustments, the proportion of supporters would be different. However, even partial switching models would yield supporter proportions between our previous bound (49.45\%) and this new estimate (78.9\%).

\section{Reinterpreting Blair et al. (2013)}

Blair et al. (2013) conducted endorsement experiments in Pakistan to measure attitudes toward militant groups. Their interpretation of the results has been influential, but it fundamentally mischaracterizes what the data reveal.

\subsection{Blair et al.'s Interpretation}

Blair et al. interpret their findings as evidence of opposition to militant groups. They write:

\begin{quote}
``We find that Pakistanis in general are \textbf{weakly negative} toward Islamist militant organizations, as shown in Table 1.''
\end{quote}

Describing their main results, they state:

\begin{quote}
``Table 1 in Panel A shows the unconditional difference in means between treatment and control groups. Each column presents the results for a particular militant group. The coefficients are negative and statistically significant at the 10\% level for all but the sectarian tanzeems, suggesting that \textbf{Pakistanis hold militant groups in low regard}.''
\end{quote}

And for their strongest effect:

\begin{quote}
``The effect is statistically and substantively strongest for the Afghan Taliban, where the treatment reduces support by 1.5\%, roughly 10\% of a standard deviation in support for policies in the control group.''
\end{quote}

\subsection{The Problem with This Interpretation}

These interpretations conflate two distinct concepts:
\begin{enumerate}
\item The \textbf{sign} of the treatment effect (negative)
\item The \textbf{level} of support for the endorsing group
\end{enumerate}

A negative treatment effect tells us that the endorsement reduced average policy support. But this does \emph{not} imply that most people oppose the endorsing group. With high baseline support, a small negative effect is fully consistent with \emph{majority support} for the group.

\subsection{The Correct Interpretation}

Using the baseline support information from Blair et al.'s own regression:
\begin{itemize}
\item Constant term (baseline support): $\alpha = 0.80$
\item Treatment effect: $\beta = -0.011$
\item Treatment group average: $\alpha + \beta = 0.789$
\end{itemize}

Under the binary switching framework, the treatment group average equals the proportion of supporters:
\begin{align}
\text{Proportion of supporters} = 0.789 = 78.9\%
\end{align}

\textbf{The data are consistent with 78.9\% of Pakistanis supporting militant groups}---not ``holding them in low regard.''

Even for the Afghan Taliban, where the treatment effect is largest ($\beta = -0.015$):
\begin{align}
\text{Proportion of supporters} = 0.80 - 0.015 = 0.785 = 78.5\%
\end{align}

This remains a substantial majority.

\subsection{Why the Sign is Misleading}

The negative sign of the ATE reflects the \emph{balance} of switchers, not the \emph{level} of support. Consider the mechanics:
\begin{itemize}
\item 78.9\% are supporters $\rightarrow$ they support the policy in treatment (outcome = 1)
\item 21.1\% are opponents $\rightarrow$ they oppose the policy in treatment (outcome = 0)
\item Treatment average = 78.9\%
\item Control average = 80\% (by assumption, mixed population)
\item ATE = 78.9\% $-$ 80\% = $-1.1$ percentage points
\end{itemize}

The negative sign arises because the treatment group average (78.9\%) is slightly lower than the control group average (80\%). This happens when there are slightly more opponents (21.1\%) than the proportion who would have opposed in control. But the \emph{level} of support---78.9\%---is a large majority.

\subsection{Summary}

Blair et al. conclude that Pakistanis are ``weakly negative'' toward militant groups and hold them in ``low regard.'' Their own data, properly interpreted, suggest the opposite: \textbf{approximately 79\% of respondents support militant groups}. The error arises from interpreting the sign of the treatment effect as an indicator of sentiment, rather than using the treatment group average to infer the proportion of supporters.

\section{Extensions and Robustness}

\subsection{From Binary to Continuous Outcomes}
The binary switching framework provides clean theoretical foundations, but many endorsement experiments use continuous outcome scales. The Blair et al. (2013) study, for instance, measured policy support on a 5-point scale rescaled to [0,1]. This requires extending our framework to continuous treatment effects.

\subsection{Asymmetric Effects}
The framework can be extended to allow for asymmetric effects where supporters and opponents shift by different magnitudes:
\begin{align}
\text{ATE} &= p \cdot X_{\text{pos}} + (1-p) \cdot (-X_{\text{neg}})
\end{align}

\subsection{Multiple Opinion Categories}
We can incorporate neutral respondents who are unaffected by endorsements:
\begin{align}
\text{ATE} &= p_{\text{support}} \cdot X_{\text{pos}} + p_{\text{oppose}} \cdot (-X_{\text{neg}}) + p_{\text{neutral}} \cdot 0
\end{align}

\subsection{Continuous Effects}

\subsubsection{Continuous Outcomes in Blair et al. (2013)}
Blair et al. (2013) measured policy support on a 5-point scale (rescaled to [0,1]). As shown in the previous section, their data ($\alpha = 0.8$, $\beta = -0.011$) imply 78.9\% support under the binary switching model. Here we extend the analysis to continuous individual effects.

Unlike the binary framework, continuous outcomes allow for a richer distribution of individual treatment effects. We can generalize our approach by allowing individual effects $\delta_i$ to take any value in $[-1, 1]$, representing the full range of possible changes on the rescaled support measure.

\subsubsection{Distributional Assumptions}
Let $\delta_i$ represent the individual treatment effect for respondent $i$, where positive values indicate the respondent supports the endorsing group (endorsement increases policy support) and negative values indicate opposition.

\textbf{Normal Distribution:}
\begin{align}
\delta_i &\sim \mathcal{N}(\mu, \sigma^2) \text{ truncated to } [-1, 1]
\end{align}

Given that the outcome is bounded in [0,1], individual effects must satisfy $\delta_i \in [-1, 1]$. With $\text{ATE} = E[\delta_i] = -0.011$, we can compute the proportion of supporters as:
\begin{align}
P(\delta_i > 0) &= P\left(\frac{\delta_i - \mu}{\sigma} > \frac{-\mu}{\sigma}\right) = 1 - \Phi\left(\frac{\mu}{\sigma}\right)
\end{align}

For example, if $\sigma = 0.05$:
\begin{align}
P(\delta_i > 0) &= 1 - \Phi\left(\frac{-0.011}{0.05}\right) = 1 - \Phi(-0.22) \approx 0.587
\end{align}

This suggests 58.7\% could be supporters despite the negative average effect.

\textbf{Beta Distribution:}
A more flexible approach uses a beta distribution rescaled to [-1, 1]:
\begin{align}
\delta_i &= 2 \cdot \text{Beta}(\alpha, \beta) - 1
\end{align}

This allows for various shapes (symmetric, skewed, U-shaped) while respecting the bounded support.

\subsubsection{Bounds Under Continuous Effects}

\textbf{Theoretical Maximum: Extreme Opponent Response}
The absolute upper bound occurs when opponents have maximal negative reactions. This generalizes our binary framework: assume
\begin{itemize}
\item Opponents: Move from full support (1) to no support (0), $\delta_{\text{opp}} = -1$
\item Supporters: Unaffected by endorsement, $\delta_{\text{supp}} = 0$
\end{itemize}

Then:
\begin{align}
\text{ATE} &= p \cdot 0 + (1-p) \cdot (-1) = -(1-p) \\
-0.011 &= -(1-p) \\
p &= 1 - 0.011 = 0.989
\end{align}

This suggests up to \textbf{98.9\% could be supporters} if opponents react maximally to terror group endorsements. Note that this bound is much higher than our binary case (49.45\%) because it assumes supporters are completely unresponsive rather than switching from 0 to 1.

\textbf{Realistic Scenario: High Baseline Support}
A more plausible scenario recognizes that Blair et al. studied benign policies (e.g., infrastructure development, polio vaccination) with naturally high baseline support. Assume:
\begin{itemize}
\item Baseline support: $y_0 = 0.9$ for both groups
\item Supporters: Maintain support, $\delta_{\text{supp}} = 0$ 
\item Opponents: Modest reduction, $\delta_{\text{opp}} = -0.1$ (from 0.9 to 0.8)
\end{itemize}

Then:
\begin{align}
\text{ATE} &= p \cdot 0 + (1-p) \cdot (-0.1) = -0.1(1-p) \\
-0.011 &= -0.1(1-p) \\
1-p &= 0.11 \\
p &= 0.89
\end{align}

This yields \textbf{89\% supporters}—still substantial despite the negative ATE.

\textbf{Alternative Realistic Scenario: Symmetric Small Effects}
If we return to a "constant swing" assumption where both groups have modest reactions of equal magnitude:
\begin{itemize}
\item Supporters: Small boost, $\delta_{\text{supp}} = +0.05$
\item Opponents: Small reduction, $\delta_{\text{opp}} = -0.05$
\end{itemize}

Then we return to our symmetric framework:
\begin{align}
\text{ATE} &= p \cdot 0.05 + (1-p) \cdot (-0.05) = 0.05(2p-1) \\
p &= \frac{\text{ATE}}{2 \times 0.05} + \frac{1}{2} = \frac{-0.011}{0.1} + 0.5 = 0.39
\end{align}

Yielding 39\% supporters. This "constant swing" model bridges our binary foundation with continuous outcomes by assuming uniform effect sizes within each group.

\subsubsection{Policy Selection for Optimal Inference}

The choice of policies dramatically affects the informativeness of endorsement experiments. Optimal policies should maximize the signal-to-noise ratio for detecting group support.

\textbf{Criteria for Policy Selection:}

\textbf{1. High Baseline Support}
Policies should have broad popular appeal (at least 80\% support) to maximize the potential for treatment effects. Suitable categories include:
\begin{itemize}
\item Public health initiatives (vaccination programs, clean water access)
\item Infrastructure development (road construction, school building)
\item Economic development programs
\end{itemize}

High baseline support ensures sufficient scope for opponents to reduce their policy support when an unpopular group provides an endorsement.

\textbf{2. Ideological Neutrality}
Researchers should avoid policies with strong ideological polarization. Contentious issues such as military spending, taxation policy, or redistributive social welfare programs confound group attitudes with partisan preferences. Instead, policies should focus on broadly valued public goods such as infrastructure, healthcare, education, and basic government services. This design choice ensures that observed effects reflect attitudes toward the endorsing group rather than pre-existing policy preferences.

\textbf{3. Endorsement Plausibility}
The endorsing group's stated support for the policy must be credible to respondents. Implausible endorsements (such as terrorist organizations endorsing gun control measures) may trigger suspicion about the experimental manipulation or create cognitive dissonance that obscures the attitude measurement. The endorsement should align with the group's known or plausible policy positions.

\textbf{4. Avoiding Ceiling Effects}
Policies with near-universal support (exceeding 95\% approval) leave limited room for opponents to express negative reactions to endorsements. Such policies may yield uninformative null effects even when substantial opposition to the endorsing group exists.

\textbf{Optimal Policy Characteristics:}
Based on these criteria, optimal policies for measuring support for controversial groups should exhibit:
\begin{itemize}
\item Baseline support levels between 80-90\%
\item Ideological neutrality (focus on public goods)
\item Plausible connection to the endorsing group's interests
\item Concrete and specific content rather than abstract principles
\end{itemize}

\textbf{Examples from Blair et al.:}
The Pakistan study's policy choices appear well-designed:
\begin{itemize}
\item Infrastructure development (high baseline support)
\item Polio vaccination (public health, not ideological)
\item Plausible for militant groups to have positions on these issues
\end{itemize}

This design likely contributed to detecting meaningful effects despite the small ATE magnitude.

\subsubsection{Empirical Distribution Estimation}
We can also estimate the distribution of individual effects non-parametrically:

\begin{enumerate}
\item Assume a flexible distributional form (e.g., mixture of normals)
\item Use the observed ATE as a moment constraint
\item Apply additional constraints from the experimental design
\item Estimate the proportion with $\delta_i > 0$
\end{enumerate}

\subsubsection{Implications for Pakistan Study}
In the Blair et al. context, the continuous framework suggests:
\begin{itemize}
\item Despite negative average sentiment toward militant groups, up to 49\% of respondents could still support them
\item The distribution of attitudes is likely heterogeneous, not bimodal
\item Small negative ATEs don't rule out substantial minority support
\item Policy implications depend critically on the shape of the attitude distribution
\end{itemize}

\subsubsection{Computational Approach for Continuous Effects}
Unlike the binary case, where supporter counts are deterministic, continuous effects allow for heterogeneous individual responses. We can use optimization methods to find the maximum number of positive shifters consistent with the observed ATE.

\textbf{Motivation:}
In the continuous Blair et al. framework, individual effects $\delta_i$ can vary within groups. Some supporters might boost policy support by +0.2, others by +0.05. This heterogeneity means we can't simply count supporters to get positive shifters.

\textbf{Optimization Framework:}
We use the Hungarian algorithm to optimally pair treatment and control responses to:
\begin{itemize}
\item Maximize the number of respondents with positive individual effects ($\delta_i > 0$)
\item Maintain the observed average treatment effect ($\bar{\delta} = -0.011$)
\item Respect realistic bounds on individual changes ($\delta_i \in [-1, 1]$)
\end{itemize}

\textbf{Algorithm:}
\begin{enumerate}
\item Generate realistic control group responses from the empirical distribution
\item Generate treatment group responses, constraining the sample average to match observed ATE
\item Create cost matrix where cost = $-1$ if $\delta_i > 0$, cost = $0$ otherwise
\item Apply Hungarian algorithm to find the optimal pairing that maximizes positive effects
\item Count positive shifters in optimal solution
\end{enumerate}

\textbf{Results for Blair et al. Parameters:}
\begin{center}
\begin{tabular}{lrrrr}
\toprule
Sample Size & Observed ATE & Max Individual Effect & Positive Shifters & Negative Shifters \\
\midrule
100 & $-0.011$ & 0.25 & 47 & 53 \\
500 & $-0.011$ & 0.25 & 236 & 264 \\
1000 & $-0.011$ & 0.25 & 472 & 528 \\
\bottomrule
\end{tabular}
\end{center}

The computational approach suggests that up to 47\% of respondents could have positive reactions to militant group endorsements, despite the negative average effect. However, this bound is much looser than our direct calculation using baseline support information (78.9\%), which suggests the optimization approach may not fully utilize available constraints.

\textbf{Reconciling the Approaches:}
The discrepancy arises because the computational approach assumes heterogeneous effect sizes without using the baseline support constraint. When we incorporate the constant term ($\alpha$ = 0.8), we get much tighter bounds that suggest substantially higher support for militant groups.

This aligns with external evidence: while direct polling shows only 9-14\% explicit support for groups like TTP, the high "don't know" rates (30-49\%) suggest many are reluctant to express true preferences in traditional surveys.

\section{Applications and Implications}

\subsection{Sensitive Survey Topics}
This framework is particularly valuable for controversial topics where direct questions suffer from social desirability bias. Endorsement experiments can reveal ``true'' support levels that traditional polling misses.

\subsection{Policy Communication}
Understanding the bounds on support helps policymakers assess whether group endorsements will help or harm policy adoption, and by how much.

\subsection{Methodological Guidance}
The bounds provide guidance on:
\begin{itemize}
\item Sample size requirements for detecting meaningful effects
\item When endorsement experiments are informative vs. inconclusive
\item How to interpret null or small effects
\end{itemize}

\section{Conclusion}

This paper develops both theoretical and computational approaches for inferring bounds on support for endorsing groups from experimental data. The key insights are:

\begin{enumerate}
\item Small average treatment effects can mask substantial heterogeneity in individual responses
\item Theoretical bounds depend critically on assumptions about maximum individual effect sizes
\item Computational methods provide empirical bounds under more realistic assumptions about effect heterogeneity
\item The framework is robust to extensions, allowing asymmetric effects and partial awareness
\end{enumerate}

Future work could apply these methods to existing endorsement experiments to reassess conclusions about public support for controversial groups and develop optimal experimental designs for maximizing inferential precision about support levels.

\end{document}